FinalManuscript_DISCS_UG

### 2018-12-12 parts/02_relatedliterature_03facialrecognition.tex
Various edits

\subsection{Haar Cascades [WIP]}
A \textit{Haar cascade classifier} is another method for facial recognition by Paul Viola and Michael Jones. It uses Haar-like features to detect regularities in a face image. A \textit{Haar-like feature} looks at a certain rectangular region of the image through a filter-like window.

\begin{figure}[!h]
    \centering
    \includegraphics[width=7cm]{figures/haarfeatures2.png}
    \caption{Examples of Haar-like features \cite{viola_robust_2004}.}
\end{figure}

A Haar-like feature is composed of black and white rectangles, and arranged such that it detects a presence or an absence of a particular image feature or regularity of interest. For example, a feature may detect the difference in intensities between the eyes and the cheeks, another feature would detect the nose bridge, and another one would detect depending on the location of the eyes. The detection is done by summing up the intensities within the black region and the white region, and then calculating the difference.

Getting the sum of pixel intensities within a region na\"{i}vely would become inefficient as the size of the rectangular region increases, so a data structure called an \textit{integral image} is used to allow more efficient detection of Haar-like features. In other words, an integral image is essentially a two-dimensional range sum that can compute sums of rectangular regions in constant time, regardless of the size of the regions.

Most of the Haar-like features are irrelevant, because a feature that works in a certain part of the image would not necessarily work in another part. The whole process may become needlessly inefficient due to computational time being potentially wasted on a huge number of irrelevant features, even though computing for a feature is said to be efficient. That is why we need to select the best features and use those to form a strong classifier in a process called AdaBoost.

In itself, a Haar feature is considered as a \textit{weak classifier}, where the probability of detecting a certain feature is slightly greater than detecting at random. Because of this, a large number of Haar features must be used together by forming them into cascade classifiers in order to achieve a sufficient enough accuracy. The resulting strong classifier would then be a linear combination of the weak classifiers.

\[h \left(x, f, p, \theta \right) = \begin{cases}1 & \text{if } pf(x) < p\theta\\ 0 & \text{otherwise}\end{cases}
\]

>>>>

% \subsection{Haar Cascades}
% A \textit{Haar cascade classifier} is another method for facial recognition by Paul Viola and Michael Jones \cite{viola_robust_2004}. It uses Haar-like features to detect regularities in a face image. A \textit{Haar-like feature} looks at a certain rectangular region of the image through a filter-like window.

% \begin{figure}[!h]
%     \centering
%     \includegraphics[width=7cm]{figures/haarfeatures2.png}
%     \caption{Examples of Haar-like features \cite{viola_robust_2004}.}
% \end{figure}

% A Haar-like feature is composed of black and white rectangles, and arranged such that it detects a presence or an absence of a particular image feature or regularity of interest. For example, a feature may detect the difference in intensities between the eyes and the cheeks, another feature would detect the edges of the face, and another one would detect depending on the location of the eyes. The detection is done by summing up the intensities within the black region and the white region, and then calculating the difference.

% Getting the sum of pixel intensities within a region na\"{i}vely would become inefficient as the size of the rectangular region increases, so a data structure called an \textit{integral image} is used to allow more efficient detection of Haar-like features. In other words, an integral image is essentially a two-dimensional range sum that can compute sums of rectangular regions in constant time, regardless of the size of the regions.

% Most of the Haar-like features are irrelevant, because a feature that works in a certain part of the image would not necessarily work in another part. The whole process may become needlessly inefficient due to computational time being potentially wasted on a huge number of irrelevant features, even though computing for a feature is said to be efficient. That is why we need to select the best features and use those to form a strong classifier in a process called AdaBoost \cite{viola_robust_2004}.

% In itself, a Haar-like feature is considered as a \textit{weak classifier}, the probability of detecting a certain feature is slightly greater than detecting at random \cite{viola_robust_2004}. So a large number of Haar-like features must be used together by forming them into cascade classifiers in order to achieve a sufficient enough accuracy. The resulting strong classifier would then be a linear combination of the weak classifiers.

% Each stage in the cascade classifier consists of weak classifiers that uses decision stumps, so that the weak classifiers can classify many examples correctly. A \textit{decision stump} can be defined as
% \[h \left(x, f, p, \theta \right) = \begin{cases}1 & \text{if } pf(x) < p\theta\\ 0 & \text{otherwise}\end{cases}
% \]
% where $x$ is a fixed window of the image, $f$ is the feature, $p$ is the polarity, and $\theta$ is the threshold \cite{viola_robust_2004}.

% Each stage also labels the region as positive (meaning that there is a face within the region), and negative (if none). If the detector sees the region as negative, it is immediately discarded and not processed anymore. Otherwise if the region is labeled as positive, it moves to the next stage for further processing. When a region successfully completes all the stages, it can be considered as a face region.

### 2018-12-12 parts/03_methodology.tex
Various edits

In this study we apply four homomorphic encryption schemes~\cite{ziad_cryptoimg:_2016, pieprzyk_efficient_2007, dasgupta_design_2016, garay_algorithms_2014} for use in image processing and facial recognition applications.
While the Paillier and DGK cryptosystems have been implemented for use in image processing in~\cite{ziad_cryptoimg:_2016, hutchison_privacy-preserving_2009}, the other cryptosystems have to be adapted for this study.

Two experiments will be conducted in this study:
\begin{enumerate}
	\item Assessment of non-linear image intensity transformations under each of the four cryptosystems.
	\item Assessment of efficiency of each of the four cryptosystems when applied for use in privacy-preserving facial recognition and detection using eigenfaces.
\end{enumerate}
The results of the image intensity transformations will be tested for image quality using benchmarks in~\cite{ahmed_benchmark_2016}.

@@

The current version of the OpenCV library (3.4.2) will be forked from the open-source GitHub repository at \url{https://github.com/opencv/opencv})~\cite{bradski_opencv_2000}.

Four homomorphic encryption schemes will be investigated. For cryptosystems with readily available open-source implementations, such implmentations will be used. For the remaining cryptosystems, the encryption and decryption methods will be implemented in Python.
\begin{itemize}
	\item The Paillier cryptosystem will be incorporated using the implementation at \url{https://github.com/n1analytics/python-paillier} developed by Data61 - CSIRO.
	\item The BGV cryptosystem will be implemented using the Pyfhel library (\url{https://github.com/ibarrond/Pyfhel}) using a HElib backend from (\url{https://github.com/shaih/HElib}).
	\item The DGK and Dasgupta--Pal cryptosystem will be implemented from scratch.
\end{itemize}

@@

For each plaintext image (PT), we will consider each image operation listed above and generate three images: a plaintext domain transformation (PDT), a ciphertext image (CT), and an encrypted domain transformation (EDT). The PDT will be generated by running the image operation on the original image. The CT will be generated by encrypting the image, then applying the operation, and the EDT will be generated by decrypting the CT. The four images (PT, PDT, CT, CDT) will then be compared using various benchmarks to evaluate the quality and security of each homomorphic encryption scheme.

@@

\subsection{Facial Recognition Tests}
%% TODO: Brian, can you fill this part up?
The method for secure facial recognition using eigenfaces by Erkin, et al. \cite{hutchison_privacy-preserving_2009-2} will be implemented for this study.
%Training data will be secured from The Database of Faces (\url{https://www.cl.cam.ac.uk/research/dtg/attarchive/facedatabase.html}) maintained by AT&T Laboratories Cambridge.
Training data will be secured from the \texttt{faces94} database (\url{https://cswww.essex.ac.uk/mv/allfaces/faces94.html}) maintained by the University of Essex.

Haar cascades will be implemented using homomorphic operations for facial detection.

Each cryptosystem will be tested on accuracy (compared to unencrypted facial detection and recognition) and processing speed.

\section{Summary}
In summary, the study will consist of
\begin{itemize}
	\item An implementation of an OpenCV library which implements the Paillier, DGK, Dasgupta--Pal, and BGV homomorphic cryptosystems.
	\item An implementation of image processing operations (intensity transformations, facial recognition) under the above cryptosystems.
	\item Conducting tests for image quality, processing time, using standard test images from~\cite{gonzalez_image_nodate}.
\end{itemize}

>>>>

In this study we apply four homomorphic encryption schemes~\cite{ziad_cryptoimg:_2016, pieprzyk_efficient_2007, dasgupta_design_2016, garay_algorithms_2014} for use in image processing and facial recognition applications.
While the Paillier and DGK cryptosystems have been implemented for use in image processing in~\cite{ziad_cryptoimg:_2016, hutchison_privacy-preserving_2009}, the other cryptosystems have to be adapted for this study.
Two experiments will be conducted in this study:
\begin{enumerate}
	\item Assessment of non-linear image intensity transformations under each of the four cryptosystems.
	\item Assessment of efficiency of each of the four cryptosystems when applied for use in privacy-preserving facial recognition and detection using eigenfaces.
\end{enumerate}
The results of the image intensity transformations will be tested for image quality using benchmarks in~\cite{ahmed_benchmark_2016}.

@@

% The current version of the OpenCV library (3.4.2) will be forked from the open-source GitHub repository at \url{https://github.com/opencv/opencv})~\cite{bradski_opencv_2000}.

Four homomorphic encryption schemes will be investigated. For cryptosystems with readily available open-source implementations, such implementations will be used. For the remaining cryptosystems, the encryption and decryption methods will be implemented in Python.
\begin{itemize}
	\item The Paillier cryptosystem will be incorporated using the implementation at \url{https://github.com/n1analytics/python-paillier} developed by Data61 - CSIRO.
	\item The BGV cryptosystem will be implemented using the Pyfhel library (\url{https://github.com/ibarrond/Pyfhel}) using a HElib backend from (\url{https://github.com/shaih/HElib}).
	\item The DGK and Dasgupta--Pal cryptosystem will be implemented from scratch.
\end{itemize}

For convenience, a wrapper library will be created that integrates the four cryptosystems into a unified interface.

@@

For each plaintext image (PT), we will consider each image operation listed above and generate three images: a plaintext domain transformation (PDT), a ciphertext image (CT), and an encrypted domain transformation (EDT). The PDT will be generated by running the image operation on the original image. The CT will be generated by encrypting the image, then applying the operation, and the EDT will be generated by decrypting the CT. The four images (PT, PDT, CT, EDT) will then be compared using various benchmarks to evaluate the quality and security of each homomorphic encryption scheme.

@@

\subsection{Facial Recognition Tests}
%% TODO: Brian, can you fill this part up? Yes
The method for secure facial recognition using eigenfaces by Erkin, et al. \cite{hutchison_privacy-preserving_2009-2} will be implemented for this study.
%Training data will be secured from The Database of Faces (\url{https://www.cl.cam.ac.uk/research/dtg/attarchive/facedatabase.html}) maintained by AT&T Laboratories Cambridge.
Training and test data will be secured from the \texttt{faces94} dataset (\url{https://cswww.essex.ac.uk/mv/allfaces/faces94.html}) maintained by the University of Essex.

% Haar cascades will be implemented using homomorphic operations for facial detection.

% Each cryptosystem will be tested on accuracy (compared to unencrypted facial detection and recognition) and processing speed.

The facial recognition tests will be done using ten-fold cross-validation for each cryptosystem, where the number of principal components used by the algorithm is fixed at $K=5$.

Prior to splitting the dataset, the images within each set are shuffled. Since there are twenty (20) images per set, two images are taken at a time for each round of cross-validation. The first round would take the first two images from each set as part of the test set, and the rest of the images will be part of the training set. Then, the succeeding round would take the next two images from each set as part of the test set. and so on until ten rounds have been done. After every cross-validation round, the accuracy score, confusion matrix, and total processing time will be obtained.

\section{Summary}
In summary, the study will consist of:
\begin{itemize}
	\item Creating a wrapper library that acts as a unified interface which implements the Paillier, DGK, Dasgupta--Pal, and BGV homomorphic cryptosystems.
	\item An implementation of image processing operations (intensity transformations, facial recognition) under the above cryptosystems.
	\item Conducting tests for image quality, processing time, using standard test images from~\cite{gonzalez_image_nodate}.
\end{itemize}
